---
title: "CUT&TAG Quality Control Report"
date: "`r format(Sys.time(), '%d %B, %Y')`"
output:
  html_document:
    theme: cosmo
    toc: true
    toc_float: true
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = FALSE, warning = FALSE, message = FALSE)
library(ggplot2)
library(dplyr)
library(tidyr)
library(knitr)
```

## Overview

This report provides quality control metrics for CUT&TAG sequencing data analysis. The metrics include fragment size distributions and Fraction of Reads in Peaks (FRiP) scores for all samples.

## Fragment Size Distribution

The fragment size distribution plot shows the size distribution of sequenced fragments for each sample. In CUT&TAG data, we typically expect to see:

- A sharp peak around 150bp representing mono-nucleosomal fragments
- Possible smaller peaks at multiples of ~150bp representing di- and tri-nucleosomal fragments

```{r fragment-sizes, fig.width=10, fig.height=6}
# Read the saved fragment size distribution plot
knitr::include_graphics("fragment_size_dist.pdf")
```

## Fraction of Reads in Peaks (FRiP)

The FRiP score indicates the percentage of reads that fall within called peaks. This metric helps assess the signal-to-noise ratio of the experiments. Higher FRiP scores generally indicate better quality data.

```{r frip-scores, fig.width=10, fig.height=6}
# Read the saved FRiP scores plot
knitr::include_graphics("frip_scores.pdf")
```

## Summary Statistics

```{r summary-stats}
# Read and display FRiP scores as a table
frip_scores <- lapply(all_samples, read_frip) %>%
    bind_rows() %>%
    mutate(
        total_reads = V3,
        reads_in_peaks = V2,
        frip_percentage = frip
    ) %>%
    select(sample = sample, total_reads, reads_in_peaks, frip_percentage)

knitr::kable(frip_scores, 
             col.names = c("Sample", "Total Reads", "Reads in Peaks", "FRiP %"),
             digits = 2)
```

## Methods

The quality control metrics were generated using the following steps:

1. Fragment size distributions were calculated from properly paired reads in BAM files
2. FRiP scores were calculated by counting the number of reads overlapping with called peaks
3. Plots were generated using ggplot2 in R

## Session Information

```{r session-info}
sessionInfo()
```
